Command line programs from LatticeRepLib

### 2023-01-10 ProgramSummary/ProgramSummary..tex
changes for HJB, mostly. And a couple of errors fixed

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{xtabular]
%\usepackage{bm}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
 \usepackage{setspace}
 \DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\BIV}[0]{$\bf{B^{4}}$}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\DXIII}[0]{$\bf{D^{13}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

			\begin{tabular}{l l l l}
				\underline{\textbf{Vector Input:}}&
				\parbox[t]{0.6\textwidth}{\textbf{g} 
					(or \textbf{v} or \textbf{g6}) for \GVI{} vectors\\
					\textbf{d} (or \textbf{d7}) for \DVII{} vectors\\
					\textbf{s} (or s6) for \SVI{}, Delone/Selling scalars\\
					\textbf{C3} for \CIII{} input (without parentheses or commas, \\
					~~~“C” would be interpreted as a C-centered unit cell)}
			\end{tabular}	\\[3pt]

@@

			\underline{\textbf{Crystal lattice input:}} 
			``\textbf{A}'', ``\textbf{B}'', ``\textbf{C}'', ``\textbf{P}'', ``\textbf{R}'', ``\textbf{F}'', ``\textbf``{I}''	\\
			~~~~~followed by three axis lengths and three angles (in degrees)\\
			\underline{\textbf{semicolon}}: 
			lines beginning with a semicolon are treated as comments\\
			\underline{\textbf{END:}} ends the data input section\\
			\bottomrule
		\end{tabular}

@@

				parts per thousand to perturb			&
				n cells perturbed normal to the input \SVI{} vector
				If a lattice centering (including P) is input,
				the output is in the same centering. Otherwise, the output is in \SVI{}.	\\[.9pt]
			CmdS6Refl	&	y	&	\SVI{}	&\hrulefill	&	For each input, 
				all 24 \SVI{} reflections are produced.\\[.9pt]
			CmdSella	&	y	&	y		&\hrulefill	&
				SELLA produces 2 output: std::out contains the match of
				each of the 24 Delone types; SVG for the Grimmer
				diagram is written to a file with a name such as 
					\verb#SEL__2023-01-07.08_56_42.svg# with date/time stamp.\\
			CmdSort		&	y	&	y		&"C3" or "seq'&	\\[.9pt]
			CmdVolume	&	y	&	mod		&\hrulefill	&		Outputs the unit cell 
				and the volume of each input cell.\\[.9pt]
			MultiMetricDists&y	& mod		&"Y/y"(optional)&	
				Parameter Y/y for maxima style output		\\[.9pt]
			PlotC3		&	y	&	mod		& 			& Plot 
				the three \CIII{} coordinates\\[.9pt]
			SELLA		&	y	&	mod		&\hrulefill	&	
				Outputs the distances from each of the Bravais lattice types 
				(in \svi{}).	\\[.9pt]
			SVD			&	y	&	mod		&\hrulefill	& Outputs the singular value decomposition vectors
				and eigenvalues for the input lattice. This is done in \SVI{}.		\\[.9pt]			
			\bottomrule

@@

>>>>

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{xtabular]
%\usepackage{bm}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
 \usepackage{setspace}
 \DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\BIV}[0]{$\bf{B^{4}}$}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\DXIII}[0]{$\bf{DC^{13}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

			\begin{tabular}{l l l l}
				\underline{\textbf{Vector Input:}}&
				\parbox[t]{0.6\textwidth}{\textbf{g} 
					 for \GVI{} vectors\\
					\textbf{s} for \SVI{}, Delone/Selling scalars\\
					\textbf{C3} for \CIII{} input (without parentheses or commas, \\
					~~~“C” would be interpreted as a C-centered unit cell)\\
					\textbf{U} for DC7 unsorted}\\
			\end{tabular}	\\[3pt]

@@

			\underline{\textbf{Crystal lattice input:}} 
			``\textbf{A}'', ``\textbf{B}'', ``\textbf{C}'', ``\textbf{P}'', ``\textbf{R}'', ``\textbf{H}'',``\textbf{F}'', ``\textbf{I}''	\\
			~~~~~followed by three axis lengths and three angles (in degrees)\\
			\underline{\textbf{semicolon}}: 
			lines beginning with a semicolon are treated as comments\\
			\underline{\textbf{END:}} ends the data input section\\
			\bottomrule
		\end{tabular}

@@

				parts per thousand to perturb			&
				n cells perturbed normal to the input \SVI{} vector
				If a lattice centering (including P) is input,
				the output is in the same centering. Otherwise, the output is in \SVI{}.	\\[.9pt]
			CmdS6Refl	&	y	&	\SVI{}	&\hrulefill	&	For each input, 
				all 24 \SVI{} reflections are produced.\\[.9pt]
			CmdSella	&	y	&	y		&\hrulefill	&
				SELLA produces 2 output: std::out contains the match of
				each of the 24 Delone types; SVG for the Grimmer
				diagram is written to a file with a name such as 
					\verb#SEL__2023-01-07.08_56_42.svg# with date/time stamp.\\
			CmdSort		&	y	&	y		&"C3" or "seq'&	\\[.9pt]
			CmdVolume	&	y	&	mod		&\hrulefill	&		Outputs the unit cell 
				and the volume of each input cell.\\[.9pt]
			MultiMetricDists&y	& mod		&"Y/y"(optional)&	
				Parameter Y/y for maxima style output		\\[.9pt]
			PlotC3		&	y	&	mod		& \hrulefill	& Plot 
				the three \CIII{} coordinates. See Figure~\ref{plotc3}.\\[.9pt]
			SELLA		&	y	&	mod		&\hrulefill	&	
				Outputs the distances from each of the Bravais lattice types 
				(in \svi{}).	\\[.9pt]
			SVD			&	y	&	mod		&\hrulefill	& Outputs the singular value decomposition vectors
				and eigenvalues for the input lattice. This is done in \SVI{}.		\\[.9pt]			
			\bottomrule

@@

	\begin{figure}
		\includegraphics[width=\textwidth]{PlotC3}
		\label{plotc3}
		\caption{Output of PlotC3}
	\end{figure}
